Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-03-01 paper_comparison/paper_comparison/paper_comparison.Rmd
subsection on hypotheses

# Estimation of p-value and power

## p-value

>>>>

# Calculation of $p$-value and power

## Hypotheses

A paragraph on what hypothesis(es) are being tested.

Generally, by looking at the residuals we are concerned with

$H_o:$ The model specification is correct

against a broad alternative that something is missing:

$H_a:$ The model specification is not correct

The conventional tests are only equipped to measure specific departures, and thus have a more specific hypotheses being tested:

XXX

## $p$-value

### 2023-03-01 paper_comparison/paper_comparison/paper_comparison.tex
subsection on hypotheses

\hypertarget{estimation-of-p-value-and-power}{%
\section{Estimation of p-value and
power}\label{estimation-of-p-value-and-power}}

\hypertarget{p-value}{%
\subsection{p-value}\label{p-value}}

@@

A primary factor contributes to the non-linearity model is the shape of
the non-linearity pattern. According to Figure
\ref{fig:poly-power-uniform-j}, conventional tests have higher power in
testing shapes constructed from lower orders of Hermite polynomials. But
the power in testing the ``Triple-U'' shape drops significantly. To
understand why this is, one needs to return to the way the RESET test is
applied. It requires a parameter indicating degree of fitted values to
test for, and the recommendation is to generically use four
(\citet{ramsey_tests_1969}). However, the ``Triple-U'' shape constructed
from the Hermite polynomials use power up to 18. If the RESET test had
been applied using a higher power no less than six, the power curve of
``Triple-U'' shape will only slight lower than the power curve of ``M''
shape. The recommendation of the polynomial power for the RESET should
be revised, perhaps. This illustrates the sensitivity of conventional
testing to the parameters, and it also points to a limitation that one
needs to know the data generating process in order to set the parameters
for the test.

For visual tests, based on the orders of the Hermite polynomials, we
expect the ``U'' shape will be the easiest one to be detected by
subjects followed by the ``S'', ``M'' and ``Triple-U'' shape. From
Figure \ref{fig:poly-power-uniform-j}, it can be observed that the power
curves are mostly aligned with our expectation, except for the ``M''
shape, which is as easy to be detected as the ``S'' shape. This implies,
unlike the conventional test, the readability of the shape do not
strictly follow the degree of the polynomials.

>>>>

\hypertarget{calculation-of-p-value-and-power}{%
\section{\texorpdfstring{Calculation of \(p\)-value and
power}{Calculation of p-value and power}}\label{calculation-of-p-value-and-power}}

\hypertarget{hypotheses}{%
\subsection{Hypotheses}\label{hypotheses}}

A paragraph on what hypothesis(es) are being tested.

Generally, by looking at the residuals we are concerned with

\(H_o:\) The model specification is correct

against a broad alternative that something is missing:

\(H_a:\) The model specification is not correct

The conventional tests are only equipped to measure specific departures,
and thus have a more specific hypotheses being tested:

XXX

\hypertarget{p-value}{%
\subsection{\texorpdfstring{\(p\)-value}{p-value}}\label{p-value}}

@@

A primary factor contributes to the non-linearity model is the shape of
the non-linearity pattern. According to Figure
\ref{fig:poly-power-uniform-j}, conventional tests have roughly the same
power in testing shapes constructed from low orders of Hermite
polynomials. But the power in testing the ``Triple-U'' shape drops
significantly. To understand why this is, one needs to return to the way
the RESET test is applied. It requires a parameter indicating degree of
fitted values to test for, and the recommendation is to generically use
four (\citet{ramsey_tests_1969}). However, the ``Triple-U'' shape
constructed from the Hermite polynomials use power up to 18. If the
RESET test had been applied using a higher power no less than six, the
power curve of ``Triple-U'' shape will only slight lower than the power
curve of ``M'' shape. The recommendation of the polynomial power for the
RESET should be revised, perhaps. This illustrates the sensitivity of
conventional testing to the parameters, and it also points to a
limitation that one needs to know the data generating process in order
to set the parameters for the test.

For visual tests, based on the orders of the Hermite polynomials, we
expect the ``U'' shape will be the easiest one to be detected by
subjects followed by the ``S'', ``M'' and ``Triple-U'' shape. From
Figure \ref{fig:poly-power-uniform-j}, it can be observed that the power
curves are mostly aligned with our expectation, except for the ``M''
shape, which is the easiest shape to be detected. This implies the
visibility of the shape do not strictly follow the degree of the
polynomials.
